\documentclass{article}


\begin{document}

\title{THE OTHER SIDE OF GUILD PRESIDENCY}
\maketitle
\section {Executive summary }{This is to enlighten people about the truth and reparations that come along side being in the seemingly smooth track of being a guild president. this struck my mind after seeing a lot of candidates in the waiting shade of guild presidency. Leadership is something everyone has to dread but to my surprise it’s not the case these days.
}
\section {Introduction} {The position holds the highest presidency in any university not makerere only but the public kind of turns a blind eye when it comes to putting its low lines into perspective. This report uncovers some of the many blows one faces in his guild presidency.
}
\section {Background} {First of all, the income you inject in as you run through your campaigns, the debts you make, the enemies you make, the brother ship ties you break, the time you spend, the lessons you miss are not at all worth the risk if really weigh the situation in immerse detail you at first think of the worst case scenario, the so called “Taiwan flight” when you literally get completely nothing after your sleepless nights and undistorted hope and struggle.} 

{
This is where most of us don’t bother thinking about in the demise of the positive thinking attitude. Secondly the best case scenario when you are elected , the feeling of being on top of the world the high life and the seemingly big but petite privileges you get courtesy of the school administration are all the people that are not in your position see but you alone know the truth of what you pass through the paper work and unavoidable circumstances put your mind at tension , the criticism you face from both your minors and superiors and believe it not this political position has a big trade off against your CGPA (lol) . research show the former 5 guild president were either discontinued, did not graduate or have an aisle of dead years. This erodes your name and field of dominance in your peers, close friends and family as opposed to what the general public sees.
}

\section {Lessons} {Let me first make this clear: “I am not in any way discouraging masses against running for the “lions rank” or in any way against it but giving students a vast perspective in there thinking may be beyond their vortex point.” 
}
\section {Conclusion}  {Run for it (guild presidency) after head wrecking planning so that you are a victor either side of the coin or if there is a lose lets kept as minimal as possible
}   
\end{document}